Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-07 csf-2017/paper.tex
public future region

{\bf Public future regions}
The public future regions relation has the following properties:
% - permanent and temporary regions stay the same type
% - public transitions
The $\perma$ and $\temp$ regions stay the same type of region and they
are allowed to take a transition in the public part of their
transition systems.

% - revoked regions can be reused as temporary regions
The $\revoked$ regions can either stay $\revoked$, or they can become
any $\temp$ region. When a region is $\revoked$ it serves as a mask
for a revoked $\temp$ region. We use masks rather than deleting the
region altogether for monotonicity reasons, but we might as well let a
new $\temp$ region serve as the mask. We do not allow $\revoked$
regions to become a $\perma$ region because we want the private future
region relation to be able to reuse any region it has revoked.

@@

>>>>

{\bf Public future regions}
In the public future regions we do not permit revocation of $\temp$
regions. In this relation, the $\temp$ and $\perma$ regions must stay
the same type and they are allowed to take a transition in the public
part of the transition system.

The $\revoked$ regions serve as masking regions, but are not as
liberal as in the private future region relation when it comes to
letting other regions replace them as masks. In the public future
region relation, we only allow $\revoked$ and $\temp$ regions to take
on the job as masking region. We have this limitation, because we
want the private future region relation to be able to reuse any region
it has revoked.

@@

Notice that the public future region relation is a subset of the
private future region relation, so anything you are allowed to do in
the public future region relation, the private future region relation
can do the same.
